Supplementary Information

### 2020-06-30 manuscript/pnas_style/supp.tex
more style edits
minor changes
incorporating extremely helpful reviewer edits. thanks!

\newcommand{\gc}[1]{{\it \color{red} #1 } }
\newcommand{\vb}[1]{{\it \color{blue} #1}}
\newcommand{\vbout}[1]{{\it \color{blue} \sout{#1}}}

@@

\begin{document}
\title{Supplementary Materials}
\author{}
\date{}
\maketitle

@@

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by $N_e$, we
develop some rough approximations here. Note, however, that since linked
selection generates temporal covariance, the overall effect is qualitatively
different than just a simple reduction in $N_e$, as drift alone cannot generate
temporal covariances.  First, we introduce some convenient notation. Let $V_{T}
= \var(p_t - p_0)$ be the total observed variation in allele frequency, $C_{LS}
= \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$ be the
contribution of all pairwise temporal covariances (observable), $V_D$ be the
unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change. Then,

\begin{align}
  V_{T} = V_{LS} + C_{LS} + V_D
\end{align}
%
Our measure $G(t)$ is then,

\begin{align}
  G(t) = \frac{C_{LS}}{V_T}
\end{align}
%
meaning we can express the fraction of total variance due to drift alone as

@@

In a neutral Wright--Fisher population, the total variation in allele
frequency change over $t$ generations is

@@

\begin{align}
  N_e \approx \frac{t p_0(1-p_0)}{2 V_T}
\end{align}

@@

\begin{align}
  G(t) \lesssim 1 - \frac{N_e}{N_{e,D}} 
\end{align}
which shows that our measure $G(t)$ is a lower bound, over much shorter
timescales, to the familiar measure $1 -
\nicefrac{\bar{\pi}}{\pi_{0}}$.

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function. The exponential fitness function corresponds to multiplicative
selection across sites and so serves as the simplest directional selection
model of a trait to understand the effects of genetic architecture on the
statistics we have used in the paper.

@@

  \caption{The temporal covariances $\cov(\Delta p_5, \Delta p_t)$ from the
    onset of selection (generation 5) to a later time point $t$, which varies
    along the x-axis, across a variety of different trait additive genetic
    variances ($V_A$, columns) and number of sites contributing to the trait
    ($L$, rows). Each point is the temporal covariance averaged over 50
    replicate simulations; dark gray points are temporal covariances after the
    onset of selection, and light gray points are before. The red line is a
    loess-smoothed curve through the covariances after the onset of selection.
    Selection on the trait was imposed through an exponential fitness function.}

@@

Overall, we confirm a finding in \textcite{Buffalo2019-io} that the initial
expected temporal covariance conditioned on $V_A$, is invariant to the number
of loci determining the trait's value, $L$ (Supplementary Figure
\ref{suppfig:sim-expfit-covs}). We do find some evidence that the decay in
temporal covariance is faster when the trait has a monogenic basis (see the
third column of Supplementary Figure \ref{suppfig:sim-expfit-covs}); this is
expected the selection coefficients are larger for these monogenic simulations,
leading to faster allele frequency changes and a rapid change in additive
genetic variance.

@@

\subsection{Temporal Covariances and $G(t)$ under Gaussian Stabilizing Selection}

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, followed by one of two two optima shift routines: (1) sudden
optima shifts of $\mu_\text{sudden} = \{0.1, 0.5, 1\}$, and (2) very graduate
optima shifts of $\mu_\text{gradual} = \{0.001, 0.01\}$ per generation using
the same two population simulation scheme described above (these shifts are
in standard deviations, since $V_S = 1$).  We used a polygenic architecture
for these simulations, with trait alleles assigned a $\pm 0.01$ effect size
with equal probability, trait mutation rate $10^{-8}$, and the optima shift
began at five generations after a $10N$ generation burnin.  Across our GSS
simulations, we see the expected selection response (Supplementary Material
Figure \ref{suppfig:gss-zbar}).

@@

Additionally, we looked at the effect the size of each replicate population
  has on a single population's $G(t)$ trajectories. These simulations had the
  same $10N$ generation burnin, followed by a change in population size
  emulating the bottlenecks associated with creating selection lines. Overall,
  we find that smaller population sizes lead to a reduced $G(t)$ (Supplementary
  Material Figure \ref{suppfig:gss-G-sampleN}). This is expected, as the
  denominator of $G(t)$ is $\var(p_t - p_0)$, which has an inverse relationship
  with $N_e$; as replicate population size is reduced, the proportion of allele
  frequency change driven by linked selection is lower, since the rate of drift
  is increased. To isolate the effects of varying replicate population size, we
  also looked at just the magnitude of temporal covariances (Supplementary
  Material Figure \ref{suppfig:gss-covs-sampleN}). We find that smaller
  replicate population sizes lead to \emph{larger} temporal covariances. We
  then looked at the initial trait variance, which as expected, does not vary
  with replicate population size (since all burnin populations had the same
  size). This implies that the linkage disequilibria is higher in smaller
populations, due to founder effects, which has the effect inflating the
temporal covariance as predicted by our theory \parencite{Buffalo2019-io}.

@@

Overall, our simulations confirm our hypotheses; see Supplementary Material
Figure \ref{suppfig:convergence-corrs}. We also find that in simulations where
we target a monogenic genetic architecture (i.e. the target number of
trait-affecting loci is $L=1$), the convergence correlations are generally much
weaker than those under a polygenic architecture. However, this effect is
mediated by the line population size; the difference in convergence correlation
between $L = 1$ and $L = 1000$ are more dissimilar when the line population
sizes are larger (compare the first column, last two rows). Like the
convergence correlations calculated on the \textcite{Barghi2019-qy} data, we
find in simulations convergence correlations decay through time. Additionally,
populations selected in opposite directions lead to negative convergence
correlations, as expected. Overall, we find that the convergence correlation is
affected by both genetic architecture and the size of the selected population
lines.

We also wanted to test whether we see similar convergence correlations under
Gaussian stabilizing selection. In these simulations, rather than targeting a
particular $V_A$, we fix the trait mutation rate at $10^{-8}$ (thus region-wide
$\theta = 2000$). Like the exponential directional selection simulations, we
impose directional selection in the same direction across the two populations
(converge), different directions (diverge), and only in one population
(single). We also vary the type (gradual versus sudden) and magnitude of optima
shifts in the two populations. Overall, simulations show convergence
correlations for the sudden optima shifts in Supplementary Figure
\ref{suppfig:convergence-corrs-gss}. Again, optima shifts in the opposite
direction cause negative convergence correlations. We found that for slow
moving optima shifts, the convergence correlations are generally too weak to be
distinguished from zero reliably, (top row of Supplementary Material Figure
\ref{suppfig:convergence-corrs-gss}).

@@

  \caption{A: The $G(t)$ averaged over 50 replicate simulations with $V_A =
    0.01$ and $L = 1000$. The blue line shows $G(t)$ calculated over ten
    generation blocks, similar to the calculation of temporal covariances of
    the \textcite{Barghi2019-qy} study. The red line shows the average $G(t)$
    estimates when the population is sampled every generation and all
    covariances can contribute to the numerator of $G(t)$. The dashed gray line
    indicates the $G(t)'$ estimate, which uses the known drift effective
    population size of the simulations. B: The temporal covariances calculated
    each generation (red line) and on ten generation blocks (blue line) using the
    same simulation data.}

@@

In our analysis of the \textcite{Barghi2019-qy} data, we describe our statistic
$G(t)$ as a lower bound for two reasons: (1) the population is sequenced every
ten generations, meaning the temporal covariances between adjacent generations
cannot contribute to the numerator of $G(t)$ but contributes to the denominator,
and (2) the estimate of $G(t)$ ignores linked selection's contribution to the
per-generation variance in allele frequency change (this is the difference
between our $G(t)$ and $G'(t)$ estimators, the latter of which includes these
variance terms \parencite{Buffalo2019-io}).  To verify that $G(t)$ estimated
every ten generations is indeed a lower bound, we used a simulation procedure
similar to the exponential fitness function simulations (described in
Supplementary Material Section \ref{supp:genetic-arch}), and calculated the
temporal covariances and $G(t)$ both each generation, and every ten
generations. Unlike the simulations described in \ref{supp:genetic-arch}, we
began selection at $10N$ generations, and used trait $V_A = 0.01$ and targeted
$L = 1000$ sites affecting the trait.

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size in our simulations at $N =
1000$ diploids, we know the drift effective population size in the absence of
selection. This allows us to estimate $G(t)'$, which is a measure of $G(t)$
that accounts for the linked selection's inflation of the variance in allele
frequency change between two generations (equation 26, \cite{Buffalo2019-io}).
Plugging in the drift effective population size $N_e = 1000$ into the
expression for $G'(t)$ and using the $\var(p_t - p_0)$ calculated for different
$t$'s, we see that $G(t)$ calculated every generation does not account for
linked selection's inflation of $\var(\Delta p_t)$ and underestimates the true
impact of linked selection as expected (dashed gray line in Supplementary
Figure \ref{suppfig:supp-blocks}A).

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
1.0, 1.5\}$. Note that for our 50Mb region, our choice of BGS $U$ parameters
are on the higher end of the spectrum expected for \emph{Drosophila}, but we
wanted to ensure the strength was sufficient to see a signal. Note that if $U
\approx 1.6$ \parencite{Elyashiv2016-vt}, and the \emph{Drosophila} genome is
$\approx 140$Mb, our region is $\approx 36\%$ of the genome; this implies a
reasonable $U$ for our region is $U \approx 0.57$, which is close to the bottom
end of our parameter range. We also vary the strength of selection against the
deleterious mutations, $s = \{0.01, 0.05, 0.1\}$, as well as different
recombination rates ($r_{bp} = \{10^{-7}, 10^{-8}\}$).  Like other simulations,
we burnin the population for $10N$ generations under backgrounds selection.
Overall, we find background selection does create temporal covariance
(Supplementary Material Figure \ref{suppfig:supp-bgs-covs}), which are stronger
under (1) higher deleterious mutation rates and (2) larger selection
coefficients. This latter point initially seems at odds with background
selection theory, as the level of pairwise diversity in a region under strong
background selection is invariant with respect to the selection coefficient.
However, looking at the background selection $G(t)$ trajectories, we find that
over time, the impact of linked selection created by background selection
appears to trend towards an equilibrium in the $r_{BP} = 10^{-7}$ subfigure,
and reaches an equilibrium in the $r_{BP} = 10^{-8}$ subfigure that seems
reasonably invariant to the choice of $s$ (Supplementary Material Figure
\ref{suppfig:supp-bgs-g-fix}). We believe that these observations can be
reconciled by $Cov(\Delta p_t,~ \Delta p_{t^{\prime}})$ being larger for larger
$s$ when $|t^{\prime}-t|$ is small, but also decaying more rapidly with
$|t^{\prime}-t|$, such that the overall contribution of selection to allele
frequency variance is invariant to $s$ (for strong background selection).
However, further future work is needed to fully explore and understand the
temporal covariance dynamics of background selection.

@@

  \caption{The trajectories of $G(t)$ through time under background selection,
    under different recombination rates ($r_{BP}$, rows), selection
    coefficients ($s$), and deleterious mutation rates ($U$). The first column
    sets $U = 1.0$, and $s$ varies, while in the second column $s=0.05$ is held
  constant, and $U$ varies. Calculated using both including fixed sites (solid
lines) and not including fixed sites (dashed lines).}

@@

Finally, we found in these background selection results that including or
excluding sites fixed or lost through time can lead  to differences in the
estimated $G(t)$ trajectories and temporal covariance. We discuss this
extensively in a subsequent section, Supplementary Materials Section
\ref{supp:fixation}.

@@

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so had a
larger long-term impact on the variance in allele frequency change.  We again
noticed fixation or loss of sites has a strong effect on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see both the effect of handling fixed/lost sites differently and the
faster rate of drift in Supplementary Materials Figure
\ref{suppfig:supp-trunc}A, where weaker truncation selection actually has
higher levels of $G(t)$. Looking just at temporal covariances, we find that
stronger truncation selection (e.g.  a smaller tail of individuals selected)
does lead to greater temporal covariances. Overall, these truncation selection
simulations demonstrate the value of considering both absolute measures of
selection's effect on allele frequency changes, i.e. temporal covariance, as
well as measures relative to drift, i.e. the $G(t)$ trajectories. While
selecting a smaller tail of individuals is associated with \emph{stronger}
selection, it also is leading to a faster rate of drift, which can distort
conclusions inferred from considering the $G(t)$ trajectories alone.

@@

\section{Supplementary Figures}

>>>>

\newcommand{\vb}[1]{{\it \color{red} #1}}
\newcommand{\vbout}[1]{{\it \color{blue} \sout{#1}}}

@@

\begin{document}

\title{Supplementary Information}
\author{Vince Buffalo and Graham Coop}
\date{}
\maketitle

\tableofcontents
\newpage

@@

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by $N_e$, we
develop some rough approximations here. Note, however, that since linked
selection generates temporal covariance, the overall effect is qualitatively
different than just a simple reduction in $N_e$, as drift alone cannot generate
temporal covariances.  First, we introduce some convenient notation. Let $V_{T}
= \var(p_t - p_0)$ be the total observed \vb{variance} in allele frequency,
$C_{LS} = \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$
be the contribution of all pairwise temporal covariances (observable), $V_D$ be
the unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change. Then,

\begin{align}
  V_{T} = V_{LS} + C_{LS} + V_D.
\end{align}
%
Our measure $G(t)$ is then,

\begin{align}
  G(t) = \frac{C_{LS}}{V_T},
\end{align}
%
meaning we can express the fraction of total variance due to drift alone as

@@

\vb{Rather than expressing this relationship in terms of variances in allele
frequencies, we can express the same relationship in terms of $N_e$.} In a
neutral Wright--Fisher population, the total variation in allele frequency
change over $t$ generations is

@@

\begin{align}
  N_e \approx \frac{t p_0(1-p_0)}{2 V_T}.
\end{align}

@@

\begin{align}
  G(t) \lesssim 1 - \frac{N_e}{N_{e,D}},
\end{align}
which shows that our measure $G(t)$ is a lower bound, over much shorter
timescales, to the familiar measure $1 -
\nicefrac{\bar{\pi}}{\pi_{0}}$.

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function \vb{(where fitness of a trait value $z$ is $w(z) \propto \exp(x)$)}.
The exponential fitness function corresponds to multiplicative selection across
sites and so serves as the simplest directional selection model of a trait to
understand the effects of genetic architecture on the statistics we have used
in the paper.

@@

  \caption{The temporal covariances $\cov(\Delta p_5, \Delta p_t)$ from the
    onset of selection (generation 5) to a later time point $t$, which varies
    along the x-axis, across a variety of different \vb{initial} trait additive
    genetic variances ($V_A$, columns) and number of sites contributing to the
    trait ($L$, rows). Each point is the temporal covariance averaged over 50
    replicate simulations; dark gray points are temporal covariances after the
    onset of selection, and light gray points are before. The red line is a
    loess-smoothed curve through the covariances after the onset of selection.
  Selection on the trait was imposed through an exponential fitness function.}

@@

Overall, we \vb{again see a} finding in \textcite{Buffalo2019-io}: that the
initial expected temporal covariance conditioned on $V_A$, is invariant to the
number of loci determining the trait's value, $L$ (Supplementary Figure
\ref{suppfig:sim-expfit-covs}). We do find some evidence that the decay in
temporal covariance is faster when the trait has a monogenic basis (see the
third column of Supplementary Figure \ref{suppfig:sim-expfit-covs}); this is
expected \vb{since} the selection coefficients are larger for these monogenic
simulations, leading to faster allele frequency changes and a rapid change in
additive genetic variance.

@@

\subsection{Temporal Covariances and $G(t)$ under Gaussian Stabilizing Selection}
\label{supp:tempcov-gss}

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, followed by one of two optimum shift routines: (1) sudden optima
shifts of $\mu_\text{sudden} = \{0.1, 0.5, 1\}$, and (2) very graduate optima
shifts of $\mu_\text{gradual} = \{0.001, 0.01\}$ per generation using the same
two population simulation scheme described above (these shifts are in standard
deviations, since $V_S = 1$).  We used a polygenic architecture for these
simulations, with trait alleles assigned a $\pm 0.01$ effect size with equal
probability, trait mutation rate $10^{-8}$, and the optima shift began at five
generations after a $10N$ generation burnin.  Across our GSS simulations, we
see the expected selection response (Supplementary Material Figure
\ref{suppfig:gss-zbar}).

@@

Additionally, we looked at the effect of the \vb{replicate population} size
\vb{drawn from the same} population has on a single population's $G(t)$
trajectories. These simulations had the same $10N$ generation burnin, followed
by a change in population size emulating the bottlenecks associated with
creating selection lines. Overall, we find that smaller population sizes lead
to a reduced $G(t)$ (Supplementary Material Figure
\ref{suppfig:gss-G-sampleN}). This is expected, as the denominator of $G(t)$ is
$\var(p_t - p_0)$, which has an inverse relationship with $N_e$; as replicate
population size is reduced, the proportion of allele frequency change driven by
linked selection is lower, since the rate of drift is increased. To isolate the
effects of varying replicate population size, we also looked at just the
magnitude of temporal covariances (Supplementary Material Figure
\ref{suppfig:gss-covs-sampleN}). We find that smaller replicate population
sizes lead to \emph{larger} temporal covariances. We then looked at the initial
trait variance, which as expected, does not vary with replicate population size
(since all burnin populations had the same size). This implies that the linkage
disequilibria is higher in smaller populations, due to founder effects, which
has the effect inflating the temporal covariance as predicted by our theory
\parencite{Buffalo2019-io}.

@@

Overall, our simulations confirm our hypotheses; see Supplementary Material
Figure \ref{suppfig:convergence-corrs}. We also find that in simulations
\vb{with} a monogenic genetic architecture (i.e. the target number of
trait-affecting loci is $L=1$), the convergence correlations are generally much
weaker than those under a polygenic architecture. However, this effect is
mediated by the line population size; the difference in convergence correlation
between $L = 1$ and $L = 1000$ are more dissimilar when the line population
sizes are larger (compare the first column, last two rows). Like the
convergence correlations calculated on the \textcite{Barghi2019-qy} data, we
find in simulations convergence correlations decay through time. Additionally,
populations selected in opposite directions lead to negative convergence
correlations, as expected. Overall, we find that the convergence correlation is
affected by both genetic architecture and the size of the selected population
lines.

We also wanted to test whether we see similar convergence correlations under
Gaussian stabilizing selection. In these simulations, rather than targeting a
particular $V_A$, we fix the trait mutation rate at $10^{-8}$ (thus region-wide
$\theta = 2000$). Like the exponential directional selection simulations, we
impose directional selection in the same direction across the two populations
(converge), different directions (diverge), and only in one population
(single). We also vary the type (gradual versus sudden) and magnitude of optima
shifts in the two populations. Overall, simulations show convergence
correlations for the sudden optima shifts in Supplementary Figure
\ref{suppfig:convergence-corrs-gss}. Again, optima shifts in the opposite
direction cause negative convergence correlations. We found that for slow
moving optima shifts, the convergence correlations are generally too weak to be
distinguished from zero reliably \vb{(not shown)}.

@@

  \caption{A: The $G(t)$ averaged over 50 replicate simulations with $V_A =
    0.01$ and $L = 1000$. The blue line shows $G(t)$ calculated over ten
    generation blocks, similar to the calculation of temporal covariances of
    the \textcite{Barghi2019-qy} study. The red line shows the average $G(t)$
    estimates when the population is sampled every generation and all
    covariances can contribute to the numerator of $G(t)$. The dashed \vb{dark}
    gray line indicates the $G'(t)$ estimate, which uses the known drift
    effective population size of the simulations. B: The temporal covariances
  calculated each generation (red line) and on ten generation blocks (blue
line) using the same simulation data.}

@@

In our analysis of the \textcite{Barghi2019-qy} data, we describe our statistic
$G(t)$ as a lower bound for two reasons: (1) the population is sequenced every
ten generations, meaning the temporal covariances between adjacent generations
cannot contribute to the numerator of $G(t)$ but contributes to the
denominator, and (2) the estimate of $G(t)$ ignores linked selection's
contribution to the per-generation variance in allele frequency change (this is
the difference between our $G(t)$ and $G'(t)$ estimators, the latter of which
\vb{is defined in \textcite{Buffalo2019-io} and} includes these variance terms.
To verify that $G(t)$ estimated every ten generations is indeed a lower bound,
we used a simulation procedure similar to the exponential fitness function
simulations (described in Supplementary Material Section
\ref{supp:genetic-arch}), and calculated the temporal covariances and $G(t)$
both each generation, and every ten generations. Unlike the simulations
described in \ref{supp:genetic-arch} \vb{where selection began at $10N+5$
generations}, selection \vb{starts at generation $10N$ here}, and used trait
$V_A = 0.01$ and targeted $L = 1000$ sites affecting the trait.

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size \vb{and reproductive sampling
scheme} in our simulations at $N = 1000$ diploids, we know the drift effective
population size in the absence of selection. This allows us to estimate
$G'(t)$, which is a measure of $G(t)$ that accounts for the linked selection's
inflation of the variance in allele frequency change between two generations
\vb{($G'(t) = 1 - \nicefrac{t\E(p_0(1-p_0))}{2 \hat{N}\var(p_t - p_0)}$  see
equation 26 of \cite{Buffalo2019-io}} for more detail).  Plugging in the drift
effective population size $N_e = 1000$ into the expression for $G'(t)$ and
using the $\var(p_t - p_0)$ calculated for different $t$'s, we see that $G(t)$
calculated every generation does not account for linked selection's inflation
of $\var(\Delta p_t)$ and underestimates the true impact of linked selection as
expected (dashed gray line in Supplementary Figure \ref{suppfig:supp-blocks}A).

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
1.0, 1.5\}$. Note that for our 50Mb region, our choice of BGS $U$ parameters
are on the higher end of the spectrum expected for \emph{Drosophila}, but we
wanted to ensure the strength was sufficient to see a signal. Note that if $U
\approx 1.6$ \parencite{Elyashiv2016-vt}, and the \emph{Drosophila} genome is
$\approx 140$Mb, our region is $\approx 36\%$ of the genome; this implies a
reasonable $U$ for our region is $U \approx 0.57$, which is close to the bottom
end of our parameter range. We also vary the strength of selection against the
deleterious mutations, $s = \{0.01, 0.05, 0.1\}$, as well as different
recombination rates ($r_{bp} = \{10^{-7}, 10^{-8}\}$).  Like other simulations,
we burnin the population for $10N$ generations under backgrounds selection.
Overall, we find background selection does create temporal covariance
(Supplementary Material Figure \ref{suppfig:supp-bgs-covs}), which are stronger
under (1) higher deleterious mutation rates and (2) larger selection
coefficients. This latter point initially seems at odds with background
selection theory, as the level of pairwise diversity in a region under strong
background selection is invariant with respect to the selection coefficient.
However, looking at the background selection $G(t)$ trajectories, we find that
over time, background selection appears to trend towards an \vb{asymptote} in
the $r_{BP} = 10^{-7}$ subfigure, and reaches an equilibrium in the $r_{BP} =
10^{-8}$ subfigure that seems reasonably invariant to the choice of $s$
(Supplementary Material Figure \ref{suppfig:supp-bgs-g-fix}). We believe that
these observations can be reconciled by $Cov(\Delta p_t,~ \Delta
p_{t^{\prime}})$ being larger for larger $s$ when $|t^{\prime}-t|$ is small,
but also decaying more rapidly with $|t^{\prime}-t|$, such that the overall
contribution of selection to allele frequency variance is invariant to $s$ (for
strong background selection).  However, further work is needed to fully explore
and understand the temporal covariance dynamics of background selection.

@@

  \caption{The trajectories of $G(t)$ through time under background selection,
    under different recombination rates ($r_{BP}$, rows), selection
    coefficients ($s$), and deleterious mutation rates ($U$). The first column
    \vb{fixes} $U = 1.0$, and $s$ varies, while in the second column $s=0.05$
    is held constant, and $U$ varies. \vb{$G(t)$ is} calculated using both
  including fixed sites (solid lines) and not including fixed sites (dashed
lines).}

@@

Finally, we found in \vb{processing these background selection simulation
results} that including or excluding sites fixed or lost through time can lead
to differences in the estimated $G(t)$ trajectories and temporal covariance. We
discuss this extensively in a subsequent section, Supplementary Materials
Section \ref{supp:fixation}.

@@

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so
\vb{have} a larger long-term impact on the variance in allele frequency change.
We again noticed fixation or loss of sites has a strong effect on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see both the effect of handling fixed/lost sites differently and the faster
rate of drift in Supplementary Materials Figure \ref{suppfig:supp-trunc}A,
where weaker truncation selection actually has higher levels of $G(t)$. Looking
just at temporal covariances, we find that stronger truncation selection (e.g.
a smaller tail of individuals selected) does lead to greater temporal
covariances. Overall, these truncation selection simulations demonstrate the
value of considering both absolute measures of selection's effect on allele
frequency changes, i.e. temporal covariance, as well as measures relative to
drift, i.e. the $G(t)$ trajectories. While selecting a smaller tail of
individuals is associated with \emph{stronger} selection, it also is leading to
a faster rate of drift, which can distort conclusions inferred from considering
the $G(t)$ trajectories alone.

@@

\section{Additional Figures}
